\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-11-01 standardmodel.tex

  \denotesS{\goodSig{\Gm}{\nu\cdot}{0}} &= \star \\
  \denotesS{\goodSig{\Gm}{\nu^+ \ \sigma \ f \ T}{n+1}} &= (\sigma, A, f, T) \\
  \denotesS{\goodTerm{\Gm}{\mu\cdot}{\cL \nu\cdot} } (\Gm) &= \star \\
  \denotesS{\goodTerm{\Gm}{\mu^+ \ o \ t}{\cL(\nu^+ \ \sigma  \ T)}} \ (\Gm)&= (o(\Gm), (\lambda \ m' . t'(\Gm, m'))) \\
  \denotesS{\goodTerm{\Gm}{p_1\mu~t}{\cL(p_1\nu~\sigma)}}(\Gm) &=  "fst"~(t\Gm) \\ 

@@

  &= \denotesS{{\Tkg {p_1\mu \ o}}}, \denotesS{(p_2\mu \ o)["sf" \ f][(id, \Tkg {p_1\mu \ o})]} \\

@@

  \denotesS{\goodWSig{\Gm}{w\cdot}{0}} &= [] \quad \text{ an empty list} \\ 
  \denotesS{\goodWSig{\Gm}{(w^+ \ A \ B \ \tau)}{n+1}}

@@

  \denotesS{\goodType{\Gm}{\pi^j_1~\tau}{}} &= "fst"~({\denotesS{\tau}}_{j})\\
  \denotesS{\goodType{\Gm, \pi^j_1~\tau}{\pi^j_2~\tau}{}} &= "snd"~({\denotesS{\tau}}_j)\\

@@

\begin{figure}[!htb]
  \centering
\begin{minipage}{0.8\linewidth}
  \begin{minted}[mathescape, escapeinside=||]{Agda}
    data MW {i}{j} (τ : |$\denotesS{\texttt{WSig i }\cdot\texttt{ S}}$|) : Set (lsuc i) where
      MWsup : |$n$| < S → (a : |$\pi^n_1$|τ) → ((|$\pi^n_2$|τ) a → MW τ) 
              → MW τ
      \end{minted}
\end{minipage}
\caption{Modeling Inductive Type}\label{fig:model-ind-type}
\end{figure}

@@

The verification of validity of this model is largely omitted here and we refer the reader to the appendix. To verify our model preserve the judgemental equality, usually unpacking the definition is enough---for example, to verify $\beta$-rule for linkage projection, we only need to see that $\denotesS{\goodTerm{\Gm}{p_1\mu~(\mu^+~o~t)}{\cL\sigma}} = \denotesS{\goodTerm{\Gm}{o}{\cL\sigma}}$ by function extensionality. One exception is for $\TyTkg{}$ and $\goodSig{\_}{\_}{n}$, the substitution law around these two are also proved together by induction because they were mutual-recursively defined together. The compatibility lemmas can be verified directly---for example $\frac{\goodSigS{\Gm}{\sigma}{n+1}\quad\goodTermS{\Gm}{o}{\cL\sigma}}{\goodTermS{\Gm}{(p_1\mu~o)}{\cL(p_1\nu~\sigma)}}$ is proved by simply unfolding the definition.

>>>>

  \denotesS{\goodSig{\Gm}{\LSigEmp}{0}} &= \star \\
  \denotesS{\goodSig{\Gm}{\LSigAdd{\sigma}{s}{T}}{n+1}} &= (\sigma, A, f, T) \\
  \denotesS{\goodTerm{\Gm}{\LkgEmp}{\cL \LSigEmp} } (\Gm) &= \star \\
  \denotesS{\goodTerm{\Gm}{\LkgAdd{o}{t}}{\cL(\LSigAdd {\sigma}{s}  {T})}} \ (\Gm)&= (o(\Gm), (\lambda \ m' . t'(\Gm, m'))) \\
  \denotesS{\goodTerm{\Gm}{\lkgproj{1}{t}}{\cL(\lsigproj{1}{\sigma})}}(\Gm) &=  "fst"~(t\Gm) \\ 

@@

  &= \denotesS{{\Tkg {\lkgproj{1}{o}}}}, \denotesS{(p_2\mu \ o)["sf" \ f][(id, \Tkg {\lkgproj{1} {o}})]} \\

@@

  \denotesS{\goodWSig{\Gm}{\WSigEmp}{0}} &= [] \quad \text{ an empty list} \\ 
  \denotesS{\goodWSig{\Gm}{(\WSigAdd{\tau}{A}{B})}{n+1}}

@@

  \denotesS{\goodType{\Gm}{\wsigproj{j}{1}{\tau}}{}} &= "fst"~({\denotesS{\tau}}_{j})\\
  \denotesS{\goodType{\Gm, \wsigproj{j}{1}{\tau}}{\wsigproj{j}{2}{\tau}}{}} &= "snd"~({\denotesS{\tau}}_j)\\

@@

\begin{figure}[!htb]
  \centering
\begin{minipage}{0.8\linewidth}
  \begin{minted}[mathescape, escapeinside=||]{Agda}
    data MW {i}{j} (τ : |$\denotesS{\texttt{WSig i }\cdot\texttt{ S}}$|) : Set (lsuc i) where
      MWsup : |$n$| < S → (a : |$\wsigproj{n}{1}{\tau}$|) → ((|$\wsigproj{n}{1}{\tau}$|τ) a → MW τ) 
              → MW τ
      \end{minted}
\end{minipage}
\caption{Modeling Inductive Type}\label{fig:model-ind-type}
\end{figure}

@@

The verification of validity of this model is largely omitted here and we refer the reader to the appendix. To verify our model preserve the judgemental equality, usually unpacking the definition is enough---for example, to verify $\beta$-rule for linkage projection, we only need to see that $\denotesS{\goodTerm{\Gm}{\lkgproj{1}{(\LkgAdd{o}{t})}}{\cL\sigma}} = \denotesS{\goodTerm{\Gm}{o}{\cL\sigma}}$ by function extensionality. One exception is for $\TyTkg{}$ and $\goodSig{\_}{\_}{n}$, the substitution law around these two are also proved together by induction because they were mutual-recursively defined together. The compatibility lemmas can be verified directly---for example $\frac{\goodSigS{\Gm}{\sigma}{n+1}\quad\goodTermS{\Gm}{o}{\cL\sigma}}{\goodTermS{\Gm}{(\lkgproj{1}{o})}{\cL(\lsigproj{1}{\sigma})}}$ is proved by simply unfolding the definition.
